Formal Modeling and Verification of a Rate-Monotonic Scheduling Implementation with Real-Time Maude

### 2016-07-09 RMS/responses.tex
corrected wrt some comments

@@

Detailed comments:

Section II.B, page 2

left column line 37-38

What are uj and vj? Are they terms too? This should be specified in
the text.

left column lines 42-46

I guess s' is the destination state. This should be specifioed in the
text.  The sentence "IR and TR together..." should not be part of the
item. It should go into a new paragraph after the list.

right column lines 22-24

As it seems the timed operators are not used, I suggest to avoid
mentioning them. By the way, this mention without any other detail is
useless.

Page 4, line 45

Why is a period of sort Nat? Shouldn't it be Counter?

>>>>

\subsection{General Comments}

@@

\subsection{Detailed Comments}

[Section II.B, page 2] left column, lines 37-38:
What are $u_j$ and $v_j$? Are they terms too? This should be specified
in the text.

Yes, they are also terms. This is specified now.

[Section II.B, page 2] left column, lines 42-46:
I guess $s'$ is the destination state. This should be specified in the
text.  The sentence "IR and TR together..." should not be part of the
item. It should go into a new paragraph after the list.

Yes, thank you for pointing this out. They are modified now.

[Section II.B, page 2] right column, lines 22-24:
As it seems the timed operators are not used, I suggest to avoid
mentioning them. By the way, this mention without any other detail is
useless.

[Page 4] line 45:
Why is a period of sort Nat? Shouldn't it be Counter?

### 2016-07-09 RMS/submission.tex
corrected wrt some comments

@@

\subsubsection{Specification}
Real-Time Maude models systems as \emph{modules}. A module specifies a
\emph{real-time rewrite theory} ${\cal R} = (\Sigma, E\cup A , IR,
TR)$, where:
\begin{itemize}
\item $\Sigma$ is an algebraic \emph{signature}, that is, a set of
  declarations of \emph{sorts}, \emph{subsorts} and \emph{function
    symbols}. The function symbols are allowed to be mixfix, in which
  case underscores ``\verb|_|'' indicate the positions of parameters.
  \emph{Terms} are expressions built from function symbols and
  variables.
\item $(\Sigma, E\cup A)$ is a \emph{membership equational logic
  theory}, with $E$ a set of \emph{conditional equations} and
  \emph{memberships} on $\Sigma$, and $A$ a set of equational axioms
  such as associativity, commutativity and identity.  $(\Sigma, E\cup
  A)$ models the system's ``static'' states as terms of some sort, and
  is equipped with a built-in specification of a sort \verb|Time|.
\item $IR$ is a set of \emph{labeled conditional rewrite rules}
  specifying the system's local transitions. Each rule has the form
  $[l]~:~t\rightarrow t'\mbox{ \textbf{if} }\bigwedge^n_{j=1}cond_j$,
  where each $cond_j$ is an equality $u_j=v_j$ and $l$ is a
  \emph{label}, $t,t'$ are terms. Such a rule specifies an
  \emph{instantaneous transition}, without consuming time, from an
  instance of $t$ to the corresponding instance of $t'$,
  \emph{provided} the conditions hold.
\item $TR$ is a set of (\emph{labeled}) \emph{tick rules} of the form
  $[l]~:~\{s\}\rightarrow\{s'\} \mbox{ \textbf{in time} }r\mbox{
  \textbf{if} }cond$ that specify \emph{timed transitions}, which
  advances time by $r$ time units in the \emph{entire} state modeled
  by term $s$. $IR$ and $TR$ together model the ``dynamic'' behaviors
  of the system.
\end{itemize}

>>>>

\usepackage{microtype}

@@

\subsubsection{Specification}
Real-Time Maude models systems as \emph{modules}. A module specifies a
\emph{real-time rewrite theory} ${\cal R} = (\Sigma, E\cup A ,
\mathit{IR}, \mathit{TR})$, where:
\begin{itemize}
\item $\Sigma$ is an algebraic \emph{signature}, that is, a set of
  declarations of \emph{sorts}, \emph{subsorts} and \emph{function
    symbols}. The function symbols are allowed to be mixfix, in which
  case underscores ``\verb|_|'' indicate the positions of parameters.
  \emph{Terms} are expressions built from function symbols and
  variables.
\item $(\Sigma, E\cup A)$ is a \emph{membership equational logic
  theory}, with $E$ a set of \emph{conditional equations} and
  \emph{memberships} on $\Sigma$, and $A$ a set of equational axioms
  such as associativity, commutativity and identity.  $(\Sigma, E\cup
  A)$ models the system's ``static'' states as terms of some sort, and
  is equipped with a built-in specification of a sort \verb|Time|.
\item $\mathit{IR}$ is a set of \emph{labeled conditional rewrite
  rules} specifying the system's local transitions. Each rule has the
  form $[l]~:~t\rightarrow t'\mbox{ \textbf{if}
  }\bigwedge^n_{j=1}cond_j$, where each $cond_j$ is an equality
  $u_j=v_j$, and $l$ is a \emph{label}, \hl{$t,t',u_j,v_j$ are terms}. Such
  a rule specifies an \emph{instantaneous transition}, without
  consuming time, from an instance of $t$ to the corresponding
  instance of $t'$, \emph{provided} the conditions hold.
\item $\mathit{TR}$ is a set of (\emph{labeled}) \emph{tick rules} of
  the form $[l]~:~\{s\}\rightarrow\{s'\} \mbox{\textbf{ in time}
  }r\mbox{ \textbf{if} }cond$ that specify \emph{timed
    transitions}. \hl{Each tick rule advances time by $r$ time units from
  the \emph{entire} state modeled by term $s$ to the destination state
  $s'$.}
\end{itemize}

\hl{$\mathit{IR}$ and $\mathit{TR}$ together model the ``dynamic''
behaviors of the system.}
